### 2019-05-11 thesis_proposal_LaTeX/Chapters/1_Introduction.tex
2nd draft Done
Grammar corrections + new document structure

\subsubsection*{\color{mygray}[Chapter ready for review]}
% Introduction to the Context where the proposal is going to be carried out.
% Describe the Problematic Situation
% Briefly describe the problem, the relevant aspects and factors that are part of it.
% Justifify the relevance to provide a solution to the problem.
% Explain what has been previoulsy done to find a solution to the problem.
% Describe the proposed solution model
% State the expected achievements by solving this problema.
% Describe the organization of the document.

Carbon nano-materials are subjected to great interest for research purposes due to their various potential applications in diverse areas that take advantage of the nano-scale properties. \cite{Siddiqui2019} Carbon nano-materials are suitable for the catalysis, adsorption, carbon capture, energy and hydrogen storage, drug delivery, bio-sensing and cancer detection. \cite{Siddiqui2019} Some matchless properties that allow carbon nano-materials to be utilized within multiple functionalities include high porosity, distinguished structures, uniform morphologies, high stability, high magnetic properties and high conductivity. \cite{Siddiqui2019}

This document bestow a thesis proposal to perform a research to engineer and design a polymer solution to achieve mass scale manufacturing of high conductive carbon nano-wires with a reduced diameter in an inexpensive, continuous, simple and reproducible manner. The research intends to involve several manufacturing processes such as near field electrospinning, photopolymerization, pyrolization and carbonization, as they have shown to be promising methods for the fabrication of carbon nano-materials. \cite{Cardenas2017} See Figure \ref{fig:fabricationFlowChart}. A number of processes have been developed for specific purposes of polymeric nano-fibers, some include surface deposition, composites, and chemical adjustments. Polymeric nano-fibers must be also pyrolyzed to generate carbon nano-wires with conductive capabilities \cite{Madou2011} for electrochemical sensing and energy storage purposes.

@@

The proposal is to continue the previous work done in regards of the synthesis of carbon nano-wires. Previous work includes the fabrication of suspended carbon nano-wires by two methods: electro-mechanical spinning and multiple-photon polymerization with a photoresist. \cite{Cardenas2017} This research proposal is intended to focus on electro-mechanical spinning processes only, to bring off polymer solutions that can be electrospun by near field electrospinning (NFES), photopolymerized and pyrolyzed into conducting carbon nano-wires. The polymer solutions described in \cite{Cardenas2017} are to be amended to achieve the goal mentioned in the previous statement.

>>>>

%\subsubsection*{\color{mygray}[Chapter ready for review]}
% Introduction to the Context where the proposal is going to be carried out.
% Describe the Problematic Situation
% Briefly describe the problem, the relevant aspects and factors that are part of it.
% Justifify the relevance to provide a solution to the problem.
% Explain what has been previoulsy done to find a solution to the problem.
% Describe the proposed solution model
% State the expected achievements by solving this problema.
% Describe the organization of the document.

Carbon nano-materials are subjected to great interest for research purposes due to their various potential applications in diverse areas that take advantage of the nano-scale properties. \cite{Siddiqui2019} Carbon nano-materials are suitable for catalysis, adsorption, carbon capture, energy and hydrogen storage, drug delivery, bio-sensing, and cancer detection. \cite{Siddiqui2019} Some matchless properties that allow carbon nano-materials to be utilized within multiple functionalities include high porosity, distinguished structures, uniform morphologies, high stability, high magnetic properties, and high conductivity. \cite{Siddiqui2019}

This document bestows a thesis proposal to perform a research to engineer and design a polymer solution to achieve mass scale manufacturing of high conductive carbon nano-wires with a reduced diameter in an inexpensive, continuous, simple and reproducible manner. The research intends to involve several manufacturing processes such as near field electrospinning, photopolymerization, pyrolization, and carbonization, as they have shown to be promising methods for the fabrication of carbon nano-materials. \cite{Cardenas2017} See Figure \ref{fig:fabricationFlowChart}. A number of processes have been developed for specific purposes of polymeric nano-fibers, some include surface deposition, composites, and chemical adjustments. Polymeric nano-fibers must be also pyrolyzed to generate carbon nano-wires with conductive capabilities \cite{Madou2011} for electrochemical sensing and energy storage purposes.

@@

The proposal is to continue the previous work done in regards to the synthesis of carbon nano-wires. Previous work includes the fabrication of suspended carbon nano-wires by two methods: electro-mechanical spinning and multiple-photon polymerization with a photoresist. \cite{Cardenas2017} This research proposal is intended to focus on electro-mechanical spinning processes only, to bring off polymer solutions that can be electrospun by near field electrospinning (NFES), photopolymerized and pyrolyzed into conducting carbon nano-wires. The polymer solutions described in \cite{Cardenas2017} are to be amended to achieve the goal mentioned in the previous statement.

### 2019-05-11 thesis_proposal_LaTeX/Chapters/2_ProblmemDefinitionAndMotivation.tex
2nd draft Done
Grammar corrections + new document structure

\subsubsection*{\color{mygray}[Chapter ready for review]}
% Describe the current situation of this problem.
% identifying the obstacles and the possible applications of your research.
% background of the problem (e.g. origins, previous attempts, etc.). 
% State the problem in detail mentioning all relative aspects, variables, relationships,
% stressing on the importance of finding a solution to the problem.

Carbon nanowires have been fabricated with a photoresist by multiple-photon polymerization techniques. However little is known about polymers that can produce conductive carbon nano-wires after pyrolysis. The lack of research relays on the fact that in the past years, it was assumed that most polymers are non-graphitic through pyrolysis \cite{Franklin1951}. In the past years photon polymerization processes have been applied to the fabrication of nano-structures with the use of a epoxy based photoresist. \cite{Boer2014} Photon polymerization techniques deliver patterning resolutions with nano-scale tolerances for the production of highly detailed structures \cite{Hribar2014}.

On the other hand, electrospinning has been acknowledged as a process with promising results at nano-structure fabrication \cite{Boer2014}, yet there is little research regarding the implementation of electrospinning for the fabrication of carbon nano-wires. Electrospinning has the potential to be a more straightforward process for the design and fabrication of nano-structures, as it can achieve mass scale manufacturing in a continuous, simple and reproducible manner. Cárdenas \cite{Cardenas2017} shows that electrospinning can be implemented with ease for carbon nano-wire synthesis. Mechano-electrospinning, a new variant of electrospinning shows promising results in the production of ordered carbon nano-wires. As stated in \cite{Cardenas2017}, mechano-electrospinning is an early technology invention, and brings new challenges, such as the reproducibility of carbon nano-wire production. Furthermore, the study of a new fabrication process to produce carbon nanowires that involves mechano-electrospinning will enable spatial control of the structures' patterning.

Since electrospinning seems to be a better alternative for carbon nano-wire fabrication processes; and for that purpose of its implementation, it is required to develop polymer solutions that can be mechano-electrospun, photopolymerized and pyrolyzed into conducting carbon nano-wires. Carbon nano-materials have been subjected to research due to their various potential applications in diverse areas that take advantage of the nano-scale properties. \cite{Siddiqui2019} Carbon nano-materials are suitable for the catalysis, adsorption, carbon capture, energy and hydrogen storage, drug delivery, bio-sensing and cancer detection. \cite{Siddiqui2019} However most applications are not currently feasible due to the lack of a continuous, simple and reproducible fabrication method with inexpensive processes. With the newly designed polymer solution, it would be possible to produce carbon nano-wires in large quantities, and therefore more applications will become feasible. On the other hand, the new technique will overcome some limitations of other methods such as lithography currently has. For instance, patterns created by lithography processes cannot be originated, only replicated, all cinstituent points of the pattern can only be addressed at the same time, and the process requires the pattern to be encoded into a mask. \cite{Landis2011}

>>>>

%\subsubsection*{\color{mygray}[Chapter ready for review]}
% Describe the current situation of this problem.
% identifying the obstacles and the possible applications of your research.
% background of the problem (e.g. origins, previous attempts, etc.). 
% State the problem in detail mentioning all relative aspects, variables, relationships,
% stressing on the importance of finding a solution to the problem.

Carbon nanowires have been fabricated with a photoresist by multiple-photon polymerization techniques. However little is known about polymers that can produce conductive carbon nano-wires after pyrolysis. The lack of research relays on the fact that in the past years, it was assumed that most polymers are non-graphitic through pyrolysis \cite{Franklin1951}. In the past years, photon polymerization processes have been applied to the fabrication of nano-structures with the use of an epoxy based photoresist. \cite{Boer2014} Photon polymerization techniques deliver patterning resolutions with nano-scale tolerances for the production of highly detailed structures \cite{Hribar2014}.

On the other hand, electrospinning has been acknowledged as a process with promising results at nano-structure fabrication \cite{Boer2014}, yet there is little research regarding the implementation of electrospinning for the fabrication of carbon nano-wires. Electrospinning has the potential to be a more straightforward process for the design and fabrication of nano-structures, as it can achieve mass scale manufacturing in a continuous, simple and reproducible manner. Cardenas \cite{Cardenas2017} shows that electrospinning can be implemented with ease for carbon nano-wire synthesis. Mechano-electrospinning, a new variant of electrospinning shows promising results in the production of ordered carbon nano-wires. As stated in \cite{Cardenas2017}, mechano-electrospinning is an early technology invention and brings new challenges, such as the reproducibility of carbon nano-wire production. Furthermore, the study of a new fabrication process to produce carbon nanowires that involves mechano-electrospinning will enable spatial control of the structures' patterning.

Since electrospinning seems to be a better alternative for carbon nano-wire fabrication processes; and for that purpose of its implementation, it is required to develop polymer solutions that can be mechano-electrospun, photopolymerized and pyrolyzed into conducting carbon nano-wires. Carbon nano-materials have been subjected to research due to their various potential applications in diverse areas that take advantage of the nano-scale properties. \cite{Siddiqui2019} Carbon nano-materials are suitable for the catalysis, adsorption, carbon capture, energy and hydrogen storage, drug delivery, bio-sensing and cancer detection. \cite{Siddiqui2019} However most applications are not currently feasible due to the lack of a continuous, simple and reproducible fabrication method with inexpensive processes. With the newly designed polymer solution, it would be possible to produce carbon nano-wires in large quantities, and therefore more applications will become feasible. On the other hand, the new technique will overcome some limitations of other methods such as lithography currently has. For instance, patterns created by lithography processes cannot be originated, only replicated, all constituent points of the pattern can only be addressed at the same time, and the process requires the pattern to be encoded into a mask. \cite{Landis2011}

### 2019-05-11 thesis_proposal_LaTeX/Chapters/3_HypothesisAndResearchQuestions.tex
Grammar corrections + new document structure

The rheological properties of polymer solutions along with synthesis parameters (stage velocity, voltage, dispense rate) can be amended through rheological analyses to obtain a low voltage electrospun-able, photopolymerizable and graphitizable fibers for the synthesis of carbon nano-wires with specified dimensions (diameter and length).

@@

\begin{itemize}
	\item{
	Is there any evidence of carbon nano-wire fabrication though electrospun-able and pyrozable polymer solutions?
	}
	\item{
	What are the process parameters to consider/control for the fabrication processes of carbon nano-wires? 
	}
	\item{
	What rheological properties are to be controlled/tested to deliver a electrospun-able and pyrozable polymer solution?	
	}
	\item{
	Are there any efforts employed to the design of polymer solutions that can be electrospun, photopolymerized, and pyrolyzed into conducting carbon nanowires?
	}
	\item{
	Are the optimal fabrication parameters defined \cite{Cardenas2017} for the synthesis of carbon nano-wires through near-field electromechanical spinning?	
	}
\end{itemize}

>>>>

The rheological properties of polymer solutions along with synthesis parameters (stage velocity, voltage, dispense rate) can be amended through rheological analyses to obtain a low voltage electrospun-able, photopolymerizable and graphitizable fibers for the synthesis of carbon nano-wires with specified dimensions (diameter and length). The rheological properties of polymer solutions along with synthesis parameters are to be amended by replacing the PEO (Poly(ethylene) oxide) component within the existing polymer solutions described in Flores \cite{Flores2017} and Cardenas \cite{Cardenas2017} work. PEO is to be replaced as its only purpose is to allow the electrospinning process to take place, but no benefit is obtained from it after pyrolysis.

@@

\begin{itemize}
	\item{
	Is there any evidence of carbon nano-wire fabrication though electrospun-able and pyrozable polymer solutions?
	}
	\item{
	What are the process parameters to consider/control for the fabrication processes of carbon nano-wires? 
	}
	\item{
	What rheological properties are to be controlled/tested to deliver an electrospun-able and pyrozable polymer solution?	
	}
	\item{
	Are there any efforts employed to the design of polymer solutions that can be electrospun, photopolymerized, and pyrolyzed into conducting carbon nanowires?
	}
	\item{
	Are the optimal fabrication parameters defined \cite{Cardenas2017} for the synthesis of carbon nano-wires through near-field electromechanical spinning?	
	}
	\item{
	What PEO-similar materials can be used to allow the electrospinning technique and favor the carbon nano-wire properties after pyrolysis? 
	}
\end{itemize}

### 2019-05-11 thesis_proposal_LaTeX/Chapters/5_StateoftheArt.tex
proposal update
Grammar corrections + new document structure

The results within Figure \ref{fig:SerieAampSweep} showed that no clear linear viscoelastic region is present. The material has influenced by small deformations, hence it is very sensible to external forces. No yield point was encountered as the moduli separate from each other with the increase of deformation.

@@

\subsection{Rheological Characterization : \textbf{Flow Curve}}
Figure \ref{fig:SerieAflowCurve} shows evidence that the equal increase of PEO and TBATFB concentrations result in an increase of shear viscosity rate $\gamma$. for concentrations from 1.00 to 0.25 $w t \%$, a slight increase of flow curve strain $\eta$ for low shear rates to 0.3 $s^{-1}$. For shear rates greater than 0.3 $s^{-1}$, the $\eta$ starts to decrease, as the polymer entanglements start to break apart, reducing friction between the polymer threads and therefore the viscosity also is reduced. The solution samples show a Newtonian-like behaviour and that may be caused by the use of the solvent cyclopentanone and by the small sized SU-8 2002 molecules.

@@

From the results in Figure \ref{fig:SerieAflowCurve}, it is noticeable that the addition of small amounts of PEO and TBATFB cause a change of one order of magnitude in shear viscosity in small concentration and a triple change in high concentrations.

@@

The flow curve results of Serie C are presented in Figure \ref{fig:SerieCflowCurve}. The sample with 1 $w t \%$ TBATFB concentration shows a shear thinning behaviour for shear rates varying between 0.1 to 15 $s^{-1}$. The 1 $w t \%$ sample describes a drop in viscosity for shear rates between 15 to 20 $s^{-1}$ followed by a stable state. A similar behaviour is observed for concentration of 0.75 $w t \%$. and less evident for 0.0 $w t \%$. For concentrations of 0.5 $w t \%$ and 0.25 $w t \%$ the behaviour of the shear viscosity is similar.

@@

Figure \ref{fig:SerieBfreqSweep} shows the frequency sweep results from Serie B. The presented behaviour is similar to Serie A. for the lower concentrations of PEO, the equipment has not enough sensibility to make measurements of the storage modulus because this one is very low. At PEO 0.25 $w t \%$, the viscosity remains almost constant at 1 $Pa s$, but as in Serie A a little variation of viscosity is presented at the lowest values of angular frequency. On the other hand, for the 0.5, 0.75 and 1.00 $w t \%$ concentrations, the viscosity is similar. At 100 $s^{-1}$, the three high concentration samples converge to 2 $Pa s$. It is imperative to assume that 0.5 $w t \%$ is the critical concentration, under this concentration the systems presents different behaviours since the molecules have enough room to diffuse and break entanglements. When the critical entanglement concentration is exceeded, the polymer threads overlap and become tangled, therefore no more entanglements are no longer possible.

@@

\begin{enumerate}
\item The thickness of the produced polymeric wires,
\item the chemical composition and viscoelasticity of the polymeric solution,
\item the molecular alignment of the polymer,
\item the heat treatment temperature,
\item the mechanical pulling on the polymer jet during electrospinning,
\item the alifnment of polymer chains induced by the presence of an electric field, and
\item the catalysts and solvents within the polymer solution.
\end{enumerate}

Cardenas reviewed different polymer fabrication techniques and materials to produce carbon nano-wires. Within Cardenas' work the following parameters were evaluated to study the desirable characteristics for building highly sensitive sensor devices: a) the chemical composition and viscoelasticity of the polymer solution, b) the thickness of the produced polymeric wires, c) the mechanical pulling on the polymeric jet during electrospinning, and d) the alignment of the polymer chains induced by the presence of an electric field. Cardenas' work states that various methods are implemented to produce nanofibers, such as laser ablation, chemical vapor deposition, discharge, and vapour growth. However, those techniques are abandoned due to their low yield output and expensive equipment. Whereas electrospinning (ES) of polymer solutions is a promising technique for simple and inexpensive fabrication of carbon nano-wires, which can be combined with a moving collector to yield even thinner fibers.

The production of carbon sstructures involves to main procedures: a) polymer patterning such as photolithography, electrospinning, Computer Numerical Control (CNC), moulding, hot embossing, and recently, Multiple Photon Polymerization; and b) carbonization, which induces further thinning of the patterned polymer and its conversion into carbon. Cardenas conducted some experiments to characterize and analyse carbon nano-wires. Polymeric SU-8 nano fibers were produced by two different methods; for each method different polymer solutions were employed.

@@

\subsection{Results and Discussion}
To test the possibility of using SU-8 to fabricate carbon nano-wires, samples were pyrolyzed in an inert environment. Samples prepared by Method 1 failed the pyrolyzation as the deposited wires were mostly liquid before carbonization. The fibers produced by Method 2 had a yeild rate of 81 $\%$. The diameters after pyrolysis were analyzed and measured using SEM micrographs.

@@

>>>>

The results within Figure \ref{fig:SerieAampSweep} showed that no clear linear viscoelastic region is present. The material has influenced by small deformations, hence it is very sensitive to external forces. No yield point was encountered as the moduli separate from each other with the increase of deformation.

@@

\subsection{Rheological Characterization : \textbf{Flow Curve}}
Figure \ref{fig:SerieAflowCurve} shows evidence that the equal increase of PEO and TBATFB concentrations result in an increase of shear viscosity rate $\gamma$. For concentrations from 1.00 to 0.25 $w t \%$, a slight increase of flow curve strain $\eta$ for low shear rates to 0.3 $s^{-1}$. For shear rates greater than 0.3 $s^{-1}$, the $\eta$ starts to decrease, as the polymer entanglements start to break apart, reducing friction between the polymer threads and therefore the viscosity also is reduced. The solution samples show a Newtonian-like behaviour and that may be caused by the use of the solvent cyclopentanone and by the small sized SU-8 2002 molecules.

@@

From the results in Figure \ref{fig:SerieAflowCurve}, it is noticeable that the addition of small amounts of PEO and TBATFB cause a change of one order of magnitude in shear viscosity in small concentrations and a triple change in high concentrations.

@@

The flow curve results of Serie C are presented in Figure \ref{fig:SerieCflowCurve}. The sample with 1 $w t \%$ TBATFB concentration shows a shear thinning behaviour for shear rates varying between 0.1 to 15 $s^{-1}$. The 1 $w t \%$ sample describes a drop in viscosity for shear rates between 15 to 20 $s^{-1}$ followed by a stable state. A similar behaviour is observed for a concentration of 0.75 $w t \%$. and less evident for 0.0 $w t \%$. For concentrations of 0.5 $w t \%$ and 0.25 $w t \%$ the behaviour of the shear viscosity is similar.

@@

Figure \ref{fig:SerieBfreqSweep} shows the frequency sweep results from Serie B. The presented behaviour is similar to Serie A. for the lower concentrations of PEO, the equipment has not enough sensibility to make measurements of the storage modulus because this one is very low. At PEO 0.25 $w t \%$, the viscosity remains almost constant at 1 $Pa s$, but as in Serie A a little variation of viscosity is presented at the lowest values of angular frequency. On the other hand, for the 0.5, 0.75 and 1.00 $w t \%$ concentrations, the viscosity is similar. At 100 $s^{-1}$, the three high concentration samples converge to 2 $Pa s$. It is imperative to assume that 0.5 $w t \%$ is the critical concentration, under this concentration the systems present different behaviours since the molecules have enough room to diffuse and break entanglements. When the critical entanglement concentration is exceeded, the polymer threads overlap and become tangled, therefore no more entanglements are no longer possible.

@@

\begin{enumerate}
\item The thickness of the produced polymeric wires,
\item the chemical composition and viscoelasticity of the polymeric solution,
\item the molecular alignment of the polymer,
\item the heat treatment temperature,
\item the mechanical pulling on the polymer jet during electrospinning,
\item the alignment of polymer chains induced by the presence of an electric field, and
\item the catalysts and solvents within the polymer solution.
\end{enumerate}

Cardenas reviewed different polymer fabrication techniques and materials to produce carbon nano-wires. Within Cardenas' work the following parameters were evaluated to study the desirable characteristics for building highly sensitive sensor devices: a) the chemical composition and viscoelasticity of the polymer solution, b) the thickness of the produced polymeric wires, c) the mechanical pulling on the polymeric jet during electrospinning, and d) the alignment of the polymer chains induced by the presence of an electric field. Cardenas' work states that various methods are implemented to produce nanofibers, such as laser ablation, chemical vapor deposition, discharge, and vapor growth. However, those techniques are abandoned due to their low yield output and expensive equipment. Whereas electrospinning (ES) of polymer solutions is a promising technique for simple and inexpensive fabrication of carbon nano-wires, which can be combined with a moving collector to yield even thinner fibers.

The production of carbon structures involves to main procedures: a) polymer patterning such as photolithography, electrospinning, Computer Numerical Control (CNC), molding, hot embossing, and recently, Multiple Photon Polymerization; and b) carbonization, which induces further thinning of the patterned polymer and its conversion into carbon. Cardenas conducted some experiments to characterize and analyze carbon nano-wires. Polymeric SU-8 nano fibers were produced by two different methods; for each method different polymer solutions were employed.

@@

\subsection{Results and Discussion}
To test the possibility of using SU-8 to fabricate carbon nano-wires, samples were pyrolyzed in an inert environment. Samples prepared by Method 1 failed the pyrolyzation as the deposited wires were mostly liquid before carbonization. The fibers produced by Method 2 had a yield rate of 81 $\%$. The diameters after pyrolysis were analyzed and measured using SEM micrographs.

@@

\section{FIND PAPER THAT CONFIRMS THAT WITH THE INCREASE OF PEO CONCENTRATION, THE POROSITY DENSITY INCREASES IN CARBON STRUCTURES AFTER PYROLYSIS. \cite{newPAPER}}

As explained in Section \ref{sec:pyrolysis}, the pyrolysis process is implemented to thermally decompose organic material into carbon. ...

### 2019-05-11 thesis_proposal_LaTeX/Chapters/6_TheoreticalFramework.tex
proposal update
Grammar corrections + new document structure

\section{Photoresists}
The electronic industry requires sustainable raw material supply for its development \cite{Sutikno2016}. Photoresists are a type of raw material used in microelectronics, which is composed by four main elements: a polymer (resin), a photoactive compound, a solvent, and an additive \cite{Schuster2009}. The additive requires to be with a low molecular weight as it is intended to act as a photosensitive material. Photoresists are used within the manufacturing process of printed circuit boards \cite{Staab2011}. Photoresists are classified into two categories. The resist is defined as positive if the radiation exposed material is soluble in photoresist developer; otherwise, for negative photoresist the exposed material remains to stay in the photoresist surface as it crosslinks upon exposure \cite{Landis2011,Sharma2012}. In the manufacturing process of a semiconductor, the radiation sources which are often used in a lithography process are ultraviolet (UV) and X-ray \cite{Mekaru2015}.

The polymeric material is available on the broad market either in liguid or solid state; \emph{MicroChem Corp.} (Westborough, MA, USA) is the principal provider of SU-8 photoresist. SU-8 and similar photoresists are inexpensive with good adhesion on the semiconductor surface and high sensitivity \cite{Staab2011}. Epoxy resins are copolymer-thermosetting plastics which are normally produced by a chemical reaction process that involves epichlorohydrin and bisphenol-A compound \cite{Singla2010}. A epoxy-based polymer is typically used to produce patterns by lithography with the application of UV radiation. Lithography is a technique to transfer patterns from a mask and then transferred onto the substrate \cite{Landis2011,Xu2014}. SU-8 is a epoxy-based negative photoresist with the advantages of being inexpensive with good mechanical properties, good chemical resistance, and good electrical isolation \cite{Xu2014}. SU-8 photoresists are used in the production processes of MEMS \cite{Zhang2001}. Photoresist-wise, the contrast and quality level of UV radiation lithography is affected by the wavelengths of radiation sources. The higher the sensitivity of the material, the better is the lithography process as it absorbs radiation energy with ease to perform photochemical reactions in forming patterns \cite{Zhang2001}.

In summary, a photoresist is a "epoxy-based resin (polymeric) material which changes its dissolution rate in a liquid solvent, called a developer, under high energy radiation.`` \cite{Landis2011}

\section{Electro-Mechanical Spinning}
Diverse polymer patterning techniques have being develop for the fabrication of nano-fibers, such as arc discharge \cite{Wang2007}, chemical vapor deposition, laser ablation \cite{Ren1998}, and vapor growth \cite{Nadarajah2008}. Nonetheless, those processes are expensive due to either the low product yield or the expensive equipment required. The electrospinning method (invented by Formhals Anton in 1934) can produce fibers with a range of diameters between 10 $n m$ and 10 $\mu m$ \cite{Jayaraman2003,Anton1930} from a polymer solution under the influence of an electrostatic force. The applied electric field and solution conductivity and viscosity is an important parameter the affects the fiber diameter during the spinning along with other parameters such as jet length, solution viscosity surrounding gas, flow rate and the collector geometry \cite{Anton1938,Larrondo1981,Baumgarten1971,Shin2001}.

Even though electrospinning is an old invention \cite{Anton1930}, it is currently a trending topic among researchers \cite{Huang2003,Reneker2008,Schiffman2008}. Some of the reasons electrospinning is to be studied is its potential to fabricate polymer nano-fibers from a variety of polymers. The technique allows the production of thin continuous fibers with ease, with diameters down to 3 $n m$ in some cases, which is something difficult to achieve by other techniques. Furthermore, the basic set-up can be modified with ease to fabricate different fibers with diversified functionalities with different materials. The produced fibers can be aligned or unaligned. Besides, the electrospinning equipment is inexpensive and of small size, compared to the equipment of standard spinning techniques. On the other hand, the understanding of the electrospinning process has improved in the last years \cite{Li2012}. As Reneker and Yarin state: "Electrospinning has rapidly changed fiber making from a capital intensive, large scale process to a low cost, broadly applicable method that manufactures fibers on a laboratory bench, to serve diverse needs ranging from materials science and technology to life sciences and clinical medicine.`` \cite{Reneker2008}

@@

Two sub-techniques can be derived from electrospinning depending on the distance between the dispensing electrode and the collector. The process in which the electrospun jet can be controlled near the tip is called NFES or near-field electrospinning. \cite{Cisquella-Serra2019} Moreover, if the distance between the collector and the dispensing needle is farther, the configuration is known as FFES or far-field electrospinning. \cite{Nataraj2012} The difference between NFES and mechano-electrospinning is the presence of a mechanical collector that allows higher precision when patterning. Figure \ref{fig:NFES} shows a typical near field mechano-electospinning apparatus.

@@

\section{Pyrolysis}
Pyrolysis is technique that involves heating of biomass in the absence of air or oxygen at a maximum pyrolysis temperature. A small amount of oxygen can burn the structures and make them unusable \cite{Pramanick2018}. Once the maximum pyrolysis temperature is reached, the temperature remains constant to produce solid char, liquids, and non-condensable products. In most cases the liquid product is the main interest of the pyrolysis process, and the properties of the pyrolysis products depend on the maximum pyrolysis temperature and the heating rate \cite{Pramanick2018,Basu2018}.

The heating of large biomass molecules results in decomposition. The pyrolysis decomposition process comprises char, liquids (condensable gases) and non-condensable gases; where the consensable gases may suffer further decomposition into non-condensable gases such as $C O$, $C O_{2}$, $H_{2}$, and $C H_{4}$. Equation \ref{eq:genPyrolysis} is a general representation of the pyrolysis decomposition reaction \cite{Basu2018}.

@@

Pyrolysis yields solid products that are more energy dense than the initial biomass, however the gas and liquid products are less energy dense \cite{Basu2018}. The liquid product of pyrolysis is usually of colour black containing hydrocarbons with a large amount of oxygen and 20\% water. When the liguid product is of interest, a rapid "quenching`` (freeze) is required after pyrolysis to prevent further decomposition or reaction with other substances \cite{Basu2018}. The solid yields of pyrolysis is usually around 85\% carbon with some oxygen, hydrogen and other substances that are present within the initial biomass \cite{Basu2018}. The biomass decomposition by pyrolysis produces non-condensable and condensable gases. The vapors (condensable gases) add up to the liquid yield of pyrolysis which is generated upon cooling. The gases (non-condensable gases) are comprised by ethylene, ethane, methane, carbon monoxide and carbon dioxide \cite{Basu2018}.

@@

Figure \ref{fig:goodbadsolvent} shows how the quality of a solvent affects the polymer distribution within the solution. Moreover the prsence of electrolites also modify the structure of the polymer threads. In non-ionic solvents, the charges are distributed along the chains and their own repulsion stretches the polimer threads into a more aligned configuration when an electrolyte is added, as detailed in Figure \ref{fig:electrolyteConcentration}.

@@

>>>>

\section{Photoresists}
The electronic industry requires a sustainable raw material supply for its development \cite{Sutikno2016}. Photoresists are a type of raw material used in microelectronics, which is composed by four main elements: a polymer (resin), a photoactive compound, a solvent, and an additive \cite{Schuster2009}. The additive requires to be with low molecular weight as it is intended to act as a photosensitive material. Photoresists are used within the manufacturing process of printed circuit boards \cite{Staab2011}. Photoresists are classified into two categories. The resist is defined as positive if the radiation exposed material is soluble in photoresist developer; otherwise, for negative photoresist the exposed material remains to stay in the photoresist surface as it crosslinks upon exposure \cite{Landis2011,Sharma2012}. In the manufacturing process of a semiconductor, the radiation sources which are often used in a lithography process are ultraviolet (UV) and X-ray \cite{Mekaru2015}.

The polymeric material is available on the broad market either in liquid or solid state; \emph{MicroChem Corp.} (Westborough, MA, USA) is the principal provider of SU-8 photoresist. SU-8 and similar photoresists are inexpensive with good adhesion on the semiconductor surface and high sensitivity \cite{Staab2011}. Epoxy resins are copolymer-thermosetting plastics which are normally produced by a chemical reaction process that involves epichlorohydrin and bisphenol-A compound \cite{Singla2010}. An epoxy-based polymer is typically used to produce patterns by lithography with the application of UV radiation. Lithography is a technique to transfer patterns from a mask and then transferred onto the substrate \cite{Landis2011,Xu2014}. SU-8 is a epoxy-based negative photoresist with the advantages of being inexpensive with good mechanical properties, good chemical resistance, and good electrical isolation \cite{Xu2014}. SU-8 photoresists are used in the production processes of MEMS \cite{Zhang2001}. Photoresist-wise, the contrast and quality level of UV radiation lithography is affected by the wavelengths of radiation sources. The higher the sensitivity of the material, the better is the lithography process as it absorbs radiation energy with ease to perform photochemical reactions in forming patterns \cite{Zhang2001}.

In summary, a photoresist is an "epoxy-based resin (polymeric) material which changes its dissolution rate in a liquid solvent, called a developer, under high energy radiation.`` \cite{Landis2011}

\section{Electro-Mechanical Spinning}
Diverse polymer patterning techniques have been developed for the fabrication of nano-fibers, such as arc discharge \cite{Wang2007}, chemical vapor deposition, laser ablation \cite{Ren1998}, and vapor growth \cite{Nadarajah2008}. Nonetheless, those processes are expensive due to either the low product yield or the expensive equipment required. The electrospinning method (invented by Formhals Anton in 1934) can produce fibers with a range of diameters between 10 $n m$ and 10 $\mu m$ \cite{Jayaraman2003,Anton1930} from a polymer solution under the influence of an electrostatic force. The applied electric field and solution conductivity and viscosity is an important parameter the affects the fiber diameter during the spinning along with other parameters such as jet length, solution viscosity surrounding gas, flow rate and the collector geometry \cite{Anton1938,Larrondo1981,Baumgarten1971,Shin2001}.

Even though electrospinning is an old invention \cite{Anton1930}, it is currently a trending topic among researchers \cite{Huang2003,Reneker2008,Schiffman2008}. One of the reasons electrospinning is to be studied is its potential to fabricate polymer nano-fibers from a variety of polymers. The technique allows the production of thin continuous fibers with ease, with diameters down to 3 $n m$ in some cases, which is something difficult to achieve by other techniques. Furthermore, the basic set-up can be modified with ease to fabricate different fibers with diversified functionalities with different materials. The produced fibers can be aligned or unaligned. Besides, the electrospinning equipment is inexpensive and of small size, compared to the equipment of standard spinning techniques. On the other hand, the understanding of the electrospinning process has improved in the last years \cite{Li2012}. As Reneker and Yarin state: "Electrospinning has rapidly changed fiber making from a capital intensive, large scale process to a low cost, broadly applicable method that manufactures fibers on a laboratory bench, to serve diverse needs ranging from materials science and technology to life sciences and clinical medicine.`` \cite{Reneker2008}

@@

Two sub-techniques can be derived from electrospinning depending on the distance between the dispensing electrode and the collector. The process in which the electrospun jet can be controlled near the tip is called NFES or near-field electrospinning. \cite{Cisquella-Serra2019} Moreover, if the distance between the collector and the dispensing needle is greater, the configuration is known as FFES or far-field electrospinning. \cite{Nataraj2012} The difference between NFES and mechano-electrospinning is the presence of a mechanical collector that allows higher precision when patterning. Figure \ref{fig:NFES} shows a typical near field mechano-electrospinning apparatus.

@@

\section{Pyrolysis} \label{sec:pyrolysis}
Pyrolysis is a technique that involves heating of biomass in the absence of air or oxygen at a maximum pyrolysis temperature. A small amount of oxygen can burn the structures and make them unusable \cite{Pramanick2018}. Once the maximum pyrolysis temperature is reached, the temperature remains constant to produce solid char, liquids, and non-condensable products. In most cases the liquid product is the main interest of the pyrolysis process, and the properties of the pyrolysis products depend on the maximum pyrolysis temperature and the heating rate \cite{Pramanick2018,Basu2018}.

The heating of large biomass molecules results in decomposition. The pyrolysis decomposition process comprises char, liquids (condensable gases) and non-condensable gases; where the condensable gases may suffer further decomposition into non-condensable gases such as $C O$, $C O_{2}$, $H_{2}$, and $C H_{4}$. Equation \ref{eq:genPyrolysis} is a general representation of the pyrolysis decomposition reaction \cite{Basu2018}.

@@

Pyrolysis yields solid products that are more energy dense than the initial biomass, however, the gas and liquid products are less energy dense \cite{Basu2018}. The liquid product of pyrolysis is usually of colour black containing hydrocarbons with a large amount of oxygen and 20\% water. When the liquid product is of interest, a rapid "quenching`` (freeze) is required after pyrolysis to prevent further decomposition or reaction with other substances \cite{Basu2018}. The solid yields of pyrolysis are usually around 85\% carbon with some oxygen, hydrogen and other substances that are present within the initial biomass \cite{Basu2018}. The biomass decomposition by pyrolysis produces non-condensable and condensable gases. The vapors (condensable gases) add up to the liquid yield of pyrolysis which is generated upon cooling. The gases (non-condensable gases) are comprised of ethylene, ethane, methane, carbon monoxide and carbon dioxide \cite{Basu2018}.

@@

Figure \ref{fig:goodbadsolvent} shows how the quality of a solvent affects the polymer distribution within the solution. Moreover the presence of electrolytes also modify the structure of the polymer threads. In non-ionic solvents, the charges are distributed along the chains and their own repulsion stretches the polymer threads into a more aligned configuration when an electrolyte is added, as detailed in Figure \ref{fig:electrolyteConcentration}.

@@

\section{Preliminary Experiments}

To verify Flores' work \cite{Flores2017}, a series of rheological measurements have been executed. Since one purpose of the proposed dissertation is to replace
